Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/1.Introduction.tex
Fluff re: Kokkos enabling cool stuff

Kokkos\footnote{from Greek for grain or seed}~\cite{KOKKOS_PAPER_HERE}, is a performance-portable, parallel programming model for C++ developed at Sandia National Laboratories (SNL). It consists of a programming model specification and a library. The specification defines execution and memory model and an application programming interface (library API). The runtime library exposes programming primitives, namely, patterns and types and maps them to the underlying abstract machine model. The machine model creates a generic view of compute hardware and memories. The Kokkos library maps execution primitives to vendor-specific programming models, libraries, and memory layouts. Kokkos has been successfully used in many large-scale projects at SNL, LLNL and other research centers~\cite{CITEKOKKOSUSECASES}. We list its key properties as follows.

@@

Further, we would like to present Kokkos to the educational community as one representative parallel programming model for a trend towards architecture-independent and performance-portable programming of CPUs and accelerators. We show a set of types that implement patterns and encapsulate data with enough semantic information to produce performance-portable, parallel code on current architectures. Further, we highlight its alignment and contributions to standardization efforts towards supporting parallel programming in C++.

>>>>

Kokkos\footnote{from Greek for grain or seed}~\cite{KOKKOS_PAPER_HERE}, is a performance-portable, parallel programming model for C++ developed at Sandia National Laboratories (SNL) for developing million line scientific software on the world\'s biggest supercomputers. It consists of a programming model specification and a library. The specification defines execution and memory model and an application programming interface (library API). The runtime library exposes functions representing parallel patterns and types for data management and maps them to the underlying abstract execution model. This execution model creates a generic view of compute hardware and memories. The Kokkos library maps execution primitives to vendor-specific programming models, libraries, and memory layouts. Kokkos has been successfully used in many large-scale projects at SNL, LLNL and other research centers~\cite{CITEKOKKOSUSECASES}. Its key properties are

@@

Further, we would like to present Kokkos to the educational community as one representative parallel programming model for a trend towards architecture-independent and performance-portable programming of CPUs and accelerators. We show an abstraction with enough semantic information to produce performance-portable, parallel code on current architectures. Further, we highlight its alignment and contributions to standardization efforts towards supporting parallel programming in C++.
